Trends of SDR in Thessaloniki 

### 2022-10-06 Article.Rmd
Commit 2022-10-06 10:17

## Data process
We take some steps in order to make the measurements comparable throughout the dataset. 
<!-- 1au -->
We adjusted all measurements to the mean distance between Sun and Earth.
<!-- TSI -->
And, we make all measurements relative to the ......TSI...... , using an homogenized timeseries of satellite TSI data.

<!-- Clear Sky -->
We will use two dataset of our measurements, one for all sky conditions (ALL), which is the whole available data, and one filtered for 'clear sky' conditions (CS). The latter was created using ..........
....

@@

>>>>

## Data process

We take some steps in order to make the measurements comparable throughout
the dataset. 
<!-- 1au -->
We adjusted all measurements to the mean distance between Sun and Earth.
<!-- TSI -->
And, we make all measurements relative to the .........TSI.......... , 
using an homogenized timeseries of satellite TSI data...........

<!-- Clear Sky -->
We will use two dataset of our measurements, one for all sky conditions (ALL),
which is the whole available data, and one filtered for 'clear sky' 
conditions (CS). The latter was created, using a method adapted to our 
site as proposed by @Long2000 and by @Reno2016.

Both dataset were aggregate in SZA bins by am, pm, am+pm

by daily mean

seasonal daily mean

Deseasonlized

## Longterm trends

@@

## SZA trends

## Trends consistency
